### 2020-04-22 serial.tex
tex

>>>>

Generation and serial intervals are under-appreciated --- often treated as auxiliary variables for estimating the reproduction number $\mathcal R$ --- yet important quantities in understanding the outset of an outbreak.
Due to their similar definitions, generation and serial intervals have been often used interchangeably even though two distributions are different.
We argue that a part of the confusion can be attributed to an apparent paradox.
As the generation-interval distribution describes the renewal process of infection, it provides a link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$;
likewise, the serial-interval distribution should describe the renewal process of symptomatic infection and therefore, should provide the same link between the epidemic growth rate $r$ and the reproduction number $\mathcal R$.
However, the current theory does not explain how two different distributions can give the same link between $r$ and $\mathcal R$ link.
We provide an answer to the paradox.
We show that serial intervals have to be defined with a reference perspective and a reference time;
the forward serial interval distribution during the exponential provides the correct link between $r$ and $\mathcal R$.
We also provide a heuristic way of addressing potential biases that can arise from not accounting for changes in these references.
Our study reveals gaps in the current understanding of serial intervals and provides rationale for reassessing serial intervals of COVID-19.
